---
title: "R programming HW1"
author: "Hyomin"
date: '2022 4 18 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## How many missing values are in the Ozone column of this data frame?
```{r}
x = read.csv('hw1_data.csv')
colSums(is.na(x))
# count NA columns
```

## What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
mean(x$Ozone, na.rm = TRUE)
```


## Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
# extract and find mean 
u <- subset(x, Ozone > 31 & Temp > 90)
mean (u$Solar.R)

```


## What is the mean of "Temp" when "Month" is equal to 6? 
```{r}
u<- subset(x, Month == 6)
mean (u$Temp)

```


## What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?

```{r}
u <- subset(x, Month == 5 & !is.na(Ozone), select = Ozone)
max(u$Ozone)

```